---
author: "Lethukuthula Nkambule"
title: "Homework 0"
format: html
editor: visual
---

### 1. Find solution(s) given values of a, b, and c

-  I define the variables and assign values to them as follows: `a=1`, `b=3`, and `c=2`

-   If `a!=0`, I define the discriminant as: $D = b^2 - 4*a*c$. Then, based on the following 3 conditions, I evaluate how many solutions there are using `if`, `else if`, `else` statements:

    -   `D > 0`, there are 2 real roots/solutions.
    -   `D == 0`, there is 1 real root/solution.
    -   `D < 0`, there are 0 real roots/solutions.

```{r}
#| echo: false

a <- 1
b <- 3
c <- 2

# make sure a != 0
if (a==0){
  cat(b, "x + ", c, " = 0\n")
  stop("a = 0, making the equation linear, not quadratic. Exiting")
}
      
D <- b^2 - 4*a*c # discriminant

if (D > 0) {
  cat(paste0("There are two real solutions for a=", a, ", b=", b, ", c=", c, ":"))
  x1 <- (-(b) - sqrt(D)) / 2*a
  x2 <- (-(b) + sqrt(D)) / 2*a
  cat(paste0("\nx = ", x1, "\nx = ", x2))
} else if (D == 0){
  cat(paste0("There is one real solution for a=", a, ", b=", b, ", c=", c, ":"))
  # x = (-b+0)/2a or (-b-0)/2a. Adding/subtracting 0 does not change num, so x = -b/2a
  x <- (-b) / (2*a)
  cat(paste0("\nx = ", x))
} else {
  cat(paste0("There are 0 real solutions for a=", a, ", b=", b, ", c=", c))
}

```

### 2. Graph of *f(x)* vs. *x* for *x* $\in$ (-5, 5)

-   I used the `seq` function to generate 300 x-values ranging from -5 to 5, then graphed *f* as a function of *x* at the different x-values using the quadratic equation from above.

```{r}
#| echo: false

x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
```
